Nengo: A Python tool for building large-scale functional brain models

### 2013-10-02 nengo.tex
Edits from Aaron's feedback

Networks are designed to be
subclasses by users,
in order to group together
parts of a model.
In most cases,
the code that creates and connects
several objects in the model can be
moved into a \texttt{Network}
subclass' \texttt{make}
function with only minor changes.

@@

A probe is used to denotes a signal
that will be recorded
throughout the simulation.
Nengo objects and connections
each have several signals that can be probed.
An ensemble's decoded value
and its neurons' spikes
can be probed, among others.

@@

\subsection{Reference simulator}

@@

The APIs of Nengo and PyNN are similar,
but differ significantly
in how groups of neurons are connected together.
In Nengo, connections commonly describe
the mathematical operation that is performed
through the connection between
two ensembles;
e.g., \texttt{DecodedConnection(A, B,
function=product)} connects ensemble A
to ensemble B, projecting the product of
some dimensions encoded by A to B.
In PyNN, connections commonly describe
features of the connection weight matrix
between two populations;
e.g., \texttt{FixedProbabilityConnector(0.5)}
connects two ensembles together,
with a probability of 0.5
that there will be a connection
between a pair of neurons in the two populations.

@@

By enabling outside contributions,
and providing a user friendly API
and many example models,
we hope to foster a rich community of modellers
contributing networks, nonlinearities,
and simulators to Nengo
and to theoretical neuroscience
as a whole.

>>>>

Networks are designed to be
subclassed by users,
in order to group together
parts of a model.
In most cases,
the code that creates and connects
several objects in the model can be
moved into a \texttt{Network}
subclass' \texttt{make}
function with only minor changes.

@@

A probe marks that a signal
will be recorded
throughout the simulation.
Nengo objects and connections
each have several signals that can be probed.
An ensemble's decoded value
and its neurons' spikes
can be probed, among others.

@@

@@

The APIs of Nengo and PyNN are similar,
but differ significantly
in how groups of neurons are connected together.
In Nengo, connections commonly describe
the mathematical operation that is performed
through the connection between
two ensembles;
e.g., \texttt{DecodedConnection(A, B,
function=product)} connects ensemble A
to ensemble B, projecting the product of
some dimensions encoded by A to B.
In PyNN, connections commonly describe
features of the connection weight matrix
between two populations;
e.g., \texttt{FixedProbabilityConnector(0.5)}
connects two ensembles together,
with a probability of 0.5
that there will be a connection
between a pair of neurons in the two populations.
This difference reflects the
fundamental difference that Nengo
is built on a theoretical framework
that enables modellers to think
about information processing in the brain
at a conceptual level.

@@

By enabling outside contributions,
and providing a user friendly API
and many example models,
we hope to foster a rich community of modellers
contributing networks, nonlinearities,
and simulators to Nengo
and to theoretical neuroscience
as a whole.
Internally, we will bring the functionality
of PyNengo to parity with JavaNengo
by implementing the use cases
not currently covered by PyNengo,
and create a graphical interface
to build models and
interactively inspect simulations.
